---
title: "W_UP_01"
author: "Rolando Benitez"
date: "Spring 2026"
output:
  html_document: default
  pdf_document: default
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(mosaic)
mydata <- read.csv(file="pushups.csv")
print(mydata)
```

# Introduction
The question is, "is who does more push ups in two minutes- playerson the line or skill position players?
data are from Georgetown varsity College football team.
data are the number of push ups done in 2 minutes (numerical, continous), position which is a categorical variable. 

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.
data are from Georgetown College football team.
data are number of push ups done in 2 minutes (numerical, continous) and position which is a categorical variable. 
# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
#favstats(pushups~position,data=mydata)
summary(mydata)
```

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

# Discussion and Conclusion
The p value comparing the two groups is .000009 this is smaller than .05 so we reject the null hypothesis and conclude we have the skill position players can do more push ups than the line players.

we reject the null hypothesis because the p value is .000009 and is less than .05
<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


